Aa Language Reference Manual

### 2018-12-12 v2/Ahir-asm/devel/docs/AaLRM.tex
Added $update note in synch.

Complete atomic statements can be explicitly sequenced using
the \$mark and \$synch constructs.  For example
\begin{verbatim}
a := (b + c) $mark FIRST
e := (f + g) $mark SECOND $synch (FIRST)
h := (i + j) $synch (FIRST SECOND)
\end{verbatim}
means that the second statement will be {\em started}
only after the first statement has {\em started}.  The
third statement will be started only after the first
two have started. This
is necessary in some cases where dependency analysis
says that two statements are independent, but you wish
to force explicit ordering.

>>>>

Complete atomic statements can be explicitly sequenced using
the \$mark and \$synch constructs.  For example
\begin{verbatim}
a := (b + c) $mark FIRST
e := (f + g) $mark SECOND $synch (FIRST)
h := (i + j) $synch ($update FIRST SECOND)
\end{verbatim}
means that the second statement will be {\em started}
only after the first statement has {\em started}.  The
third statement will be started only after the first
has finished and the second has started. This
is necessary in some cases where dependency analysis
says that two statements are independent, but you wish
to force explicit ordering.
